---
title: "Additional analysis in relation to iconicity ratings"
author: "Bodo"
date: "19/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Preprocessing

Load package:

```{r, warning = FALSE, message = FALSE}
library(tidyverse)
library(effsize)
```

## Re-analysis of data from Thompson et al. (2020)

Load data:

```{r, message = FALSE, warning = FALSE}
icon <- read_csv('English_Iconicity_Ratings.csv')
```


Average ratings by word, keeping stratum and etymology columns:

```{r}
avgs <- icon %>% group_by(word, stratum, etymology) %>% 
  summarize(rating = mean(rating))
```

Get subset of Germanic words:

```{r}
ger <- filter(avgs, stratum == 'Germanic')
```

## Analysis of imitative versus non-imitative origin with Thompson et al.'s data:

Check means:

```{r}
ger %>% group_by(etymology) %>% 
  summarize(M = mean(rating))
```

Plot this:

```{r, width = 4, height = 7}
ger %>% ggplot(aes(x = etymology, fill = etymology, y = rating)) +
  geom_boxplot() +
  scale_fill_brewer(palette = 'Spectral') +
  theme_minimal()
```

Perform a t-test of this:

```{r}
with(ger, t.test(rating ~ etymology, var.equal = TRUE))
```

What is the effect size of thsi?

```{r}
with(ger, cohen.d(rating ~ etymology, var.equal = TRUE))
```


## Analysis of Winter (2016) data:

Load packages and data:

```{r, message = FALSE, warning = FALSE}
icon <- read_csv('iconicity_ratings.csv') # winter et al. 2017 ratings
OED <- read_csv('all_words_OED_etymology.csv') # OED etymologies from winter 2016
```

Join datasets:

```{r}
OED <- left_join(OED, icon)
```

Check number of origins:

```{r}
table(OED$Origin)
```

Recode to make groupings in analogy to Thompson et al. — those of suspected imitative origin are coded as imitative (doesn't change much if these are re-assigned):

```{r}
OED <- mutate(OED,
              OriginFull = Origin,
              Origin = ifelse(Origin == 'Anglo-Norman', 'other', Origin),
              Origin = ifelse(Origin == 'French borrowing', 'French', Origin),
              Origin = ifelse(Origin == 'Germanic, perhaps ultimatively imitative', 'imitative', Origin),
              Origin = ifelse(Origin == 'Germanic/probably imitative', 'imitative', Origin),
              Origin = ifelse(Origin == 'Greek borrowing', 'other', Origin),
              Origin = ifelse(Origin == 'Italian borrowing', 'other', Origin),
              Origin = ifelse(Origin == 'Morocco', 'other', Origin),
              Origin = ifelse(Origin == 'Old Norse', 'other', Origin),
              Origin = ifelse(Origin == 'origin unknown', 'unclear', Origin),
              Origin = ifelse(Origin == 'possibly Celtic ', 'other', Origin),
              Origin = ifelse(Origin == 'probably Germanic ', 'Germanic', Origin),
              Origin = ifelse(Origin == 'probably Old Norse', 'other', Origin),
              Origin = ifelse(Origin == 'probably Scandinavian', 'other', Origin),
              Origin = ifelse(Origin == 'Spanish', 'other', Origin),
              Origin = ifelse(Origin == 'Scandinavian', 'other', Origin),
              Origin = ifelse(Origin == 'Scottish', 'other', Origin),
              Origin = ifelse(Origin == 'probably Dutch', 'other', Origin),
              Origin = ifelse(Origin == 'probably Spanish', 'other', Origin),
              Origin = ifelse(Origin == 'probably French', 'French', Origin),
              Origin = ifelse(Origin == 'probably Germanic', 'Germanic', Origin),
              Origin = ifelse(Origin == 'probably Latin', 'Latin borrowing', Origin),
              Origin = ifelse(Origin == 'French borrowing', 'French', Origin),
              Origin = ifelse(Origin == 'possibly French borrowing', 'French', Origin),
              Origin = ifelse(Origin == 'possibly imitative', 'imitative', Origin),
              Origin = ifelse(Origin == 'possibly Celtic', 'other', Origin),
              Origin = ifelse(Origin == 'probably imitative', 'imitative', Origin),
              Origin = ifelse(Origin == 'Spanish borrowing', 'other', Origin),
              Origin = ifelse(Origin == 'unclear, partly imitative', 'imitative', Origin),
              Origin = ifelse(Origin == 'unclear, probably Scandinavian', 'other', Origin),
              Origin = ifelse(Origin == 'Urdu', 'other', Origin))
```

Check again:

```{r}
table(OED$Origin)
```

Test the iconicity effect:

```{r}
xmdl <- lm(Iconicity ~ Origin, data = OED)
anova(xmdl)
summary(xmdl)
```

Do an imitative versus rest:

```{r}
OED <- mutate(OED, ImitativeOrNot = ifelse(Origin == 'imitative', 'imitative', 'not_imitative'))
```

Test this:

```{r}
t.test(Iconicity ~ ImitativeOrNot, data = OED, var.equal = TRUE)
```

Also effect size:

```{r}
cohen.d(Iconicity ~ ImitativeOrNot, data = OED, var.equal = TRUE)
```

Perform post-hoc comparisons:

```{r}
myaov <- aov(Iconicity ~ Origin, data = OED)
TukeyHSD(myaov)
```












